\section{Purpose}
Currently, with creative fields being as saturated as they are, 
it is difficult for a newcomer into the "service arts", such as photography, commision painting, and singing,
to find clientele. The typical creative has difficulty marketing their services, and this is likely because 
their services are not being marketed "properly". In agile software development, there is an emphasis on 
finding a demographic of people to solve a problem for, and then developing a product that acts as a solution
to that problem. With this methodology, the organization developing the product has sought out and matched their target clientele.

However, in more "creative-oriented" fields, this does not seem to be the representative approach. The default approach from the 
creative seems to be to cast a wide net so to speak, and hopefully net some buyers.

If it were possible to filter/pre-select potential clients on some objective and/or measurable metric, the artist 
would presumably have higher success pitching themselves the clients with whom they "match".

\section{Scope}
The scope of this project thus far is to be used as a photographer looking for likely candidates for clientele,
using social media. Specifically, the product would allow a photographer to single out people that are interested in the genres that the 
photographer is seeking to shoot, based on hashtags, thereby facilitating the filtering process for the photographer.

\section{Overview}
A representative use-case for the product is given below:

1. The user signs into \serviceName with their Instagram account.

2. The user searches hashtags matching what they want to take pictures of.

3. The user gets a curated list of potential clients that they can then contact.

\section{Reference Material}
\section{Definitions and Acronyms}
\begin{table}[ht]
    \centering
    \begin{tabular}{l | l}
        Term & Definition \\
        \hline
        IG & Instagram \\
        FB & Facebook \\
        IGAPI & Instagram Platform API \\
        FBGA & Facebook Graph API \\
        FBBDA & Facebook Basic Display API \\
        MVP & Minimum Viable Product \\
    \end{tabular}
    \caption{Table of Definitions and acronyms used}
    \label{tab: def_ac}
\end{table}



% \blindtext[6]